Exploiting the Social Graph: Increasing Engagement via Collaborative Interactive Evolution

### 2017-03-10 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Authors corrected
Figure 6 deleted.

\author{\IEEEauthorblockN{Mario Garc\'ia-Valdez, Amaury Hern\'andez-\'Aguila, Alejandra Mancilla}
\IEEEauthorblockA{Instituto Tecnol\'ogico de Tijuana\\
Tijuana, Mexico\\
Email: (mario,amherag)@tectijuana.edu.mx,alejandra.mancilla@gmail.com}
\and
\IEEEauthorblockN{Juan Juli\'an Merelo Guerv\'os}
\IEEEauthorblockA{Universidad de Granada, CITIC\\
Email: jmerelo@geneura.ugr.es}
}

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_2.png}
    \caption{User network view of the Base deployment}
    \label{fig:B-network}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_3.png}
    \caption{User network view of the Graph Gamification deployment}
    \label{fig:GG-network}
\end{figure}
\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.3in]{img/comparison.png}
    \caption{Users ranked by the number of phenotypes they rated vs. the number of phenotypes evaluated using a logarithmic scale. } % Explain a little more and label axes. The
                         % three lines have the same label,
                         % "participation". Not too clear - JJ
                         % Done - Mario
    \label{fig:top-ranked-participation}
\end{figure*}

When monitoring the experiments by querying the graph database,  the Cypher query language 
provided interesting views on the data that it would have been
difficult to replicate with a relational database. 
For instance, to compare the number of volunteers in deployments
B and GG (shown in figures \ref{fig:B-network} and \ref{fig:GG-network} respectively)  a simple query
provided a view of the social network of volunteers.

>>>>

\author{\IEEEauthorblockN{Mario Garc\'ia-Valdez, Jos\'e Christian Romero, Alejandra Mancilla}
\IEEEauthorblockA{Instituto Tecnol\'ogico de Tijuana\\
Tijuana, Mexico\\
Email: (mario,amherag)@tectijuana.edu.mx,alejandra.mancilla@gmail.com}
\and
\IEEEauthorblockN{Juan Juli\'an Merelo Guerv\'os}
\IEEEauthorblockA{Universidad de Granada, CITIC\\
Email: jmerelo@geneura.ugr.es}
}

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_2.png}
    \caption{User network view of the Base deployment}
    \label{fig:B-network}
\end{figure}
\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.3in]{img/comparison.png}
    \caption{Users ranked by the number of phenotypes they rated vs. the number of phenotypes evaluated using a logarithmic scale. } % Explain a little more and label axes. The
                         % three lines have the same label,
                         % "participation". Not too clear - JJ
                         % Done - Mario
    \label{fig:top-ranked-participation}
\end{figure*}

When monitoring the experiments by querying the graph database,  the Cypher query language 
provided interesting views on the data that it would have been
difficult to replicate with a relational database, for instance, to show the social network of volunteers 
as shown in figure \ref{fig:B-network}.
